Randomization Examples using `nycflights13` `flights` data

### 2018-03-23 inst/doc/flights_examples.Rmd
Update pkgdown and vignettes

```{r}
x_bar <- fli_small %>%
  summarize(mean(dep_delay)) %>%
  pull()
null <- fli_small %>%
  specify(response = dep_delay) %>%
  hypothesize(null = "point", mu = 10) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "mean")
ggplot(null, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = x_bar, color = "red")
null %>%
  summarize(p_value = mean(stat > x_bar) * 2)
```

@@

```{r}
x_tilde <- fli_small %>%
  summarize(median(dep_delay)) %>%
  pull()
null <- fli_small %>%
  specify(response = dep_delay) %>%
  hypothesize(null = "point", med = 0) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "median")
ggplot(null, aes(x = stat)) +
  geom_bar() +
  geom_vline(xintercept = x_tilde, color = "red")
null %>%
  summarize(p_value = mean(stat < x_tilde) * 2)
```

@@

```{r}
p_hat <- fli_small %>%
  summarize(mean(day_hour == "morning")) %>%
  pull()
null <- fli_small %>%
  specify(response = day_hour, success = "morning") %>%
  hypothesize(null = "point", p = .5) %>%
  generate(reps = 1000, type = "simulate") %>%
  calculate(stat = "prop")
ggplot(null, aes(x = stat)) +
  geom_bar() +
  geom_vline(xintercept = p_hat, color = "red")
null %>%
  summarize(p_value = mean(stat < p_hat) * 2)
```

@@

```{r}
null <- fli_small %>%
  mutate(day_hour_logical = (day_hour == "morning")) %>%
  specify(response = day_hour_logical, success = "TRUE") %>%
  hypothesize(null = "point", p = .5) %>%
  generate(reps = 1000, type = "simulate") %>%
  calculate(stat = "prop")
```

@@

```{r}
d_hat <- fli_small %>%
  group_by(season) %>%
  summarize(prop = mean(day_hour == "morning")) %>%
  summarize(diff(prop)) %>%
  pull()
null <- fli_small %>%
  specify(day_hour ~ season, success = "morning") %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>% 
  calculate(stat = "diff in props", order = c("summer", "winter"))
ggplot(null, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = d_hat, color = "red")
null %>%
  summarize(p_value = mean(stat < d_hat) * 2)
```

@@

```{r}
Chisq_hat <- chisq.test(table(fli_small$origin))$stat
null <- fli_small %>%
  specify(response = origin) %>%
  hypothesize(null = "point", 
              p = c("EWR" = .33, "JFK" = .33, "LGA" = .34)) %>% 
  generate(reps = 1000, type = "simulate") %>% 
  calculate(stat = "Chisq")
ggplot(null, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = Chisq_hat, color = "red")
null %>%
  summarize(p_value = mean(stat > Chisq_hat)) 
```

@@

```{r}
Chisq_hat <- chisq.test(table(fli_small$day_hour, fli_small$origin))$stat
null <- fli_small %>%
  specify(day_hour ~ origin) %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>% 
  calculate(stat = "Chisq")
ggplot(null, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = Chisq_hat, color = "red")
null %>%
  summarize(p_value = mean(stat > Chisq_hat)) 
```

@@

```{r}
d_hat <- fli_small %>% 
  group_by(season) %>% 
  summarize(mean_stat = mean(dep_delay)) %>% 
  summarize(diff(mean_stat)) %>% 
  pull()
null <- fli_small %>%
  specify(dep_delay ~ season) %>% # alt: response = dep_delay, 
  # explanatory = season
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("summer", "winter"))
ggplot(null, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = d_hat, color = "red")
null %>%
  summarize(p_value = mean(stat > d_hat) * 2)   
```

@@

```{r}
d_hat <- fli_small %>% 
  group_by(season) %>% 
  summarize(median_stat = median(dep_delay)) %>% 
  summarize(diff(median_stat)) %>% 
  pull()
null <- fli_small %>%
  specify(dep_delay ~ season) %>% # alt: response = dep_delay, 
  # explanatory = season
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in medians", order = c("summer", "winter"))
ggplot(null, aes(x = stat)) +
  geom_bar() +
  geom_vline(xintercept = d_hat, color = "red")
null %>%
  summarize(p_value = mean(stat > d_hat) * 2)    
```

@@

```{r}
F_hat <- anova(
               aov(formula = arr_delay ~ origin, data = fli_small)
               )$`F value`[1]
null <- fli_small %>%
   specify(arr_delay ~ origin) %>% # alt: response = arr_delay, 
   # explanatory = origin
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "F")
ggplot(null, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = F_hat, color = "red")  
null %>% 
  summarize(p_value = mean(stat > F_hat))
```

@@

```{r}
slope_hat <- lm(arr_delay ~ dep_delay, data = fli_small) %>% 
  broom::tidy() %>% 
  filter(term == "dep_delay") %>% 
  select(estimate) %>% 
  pull()
null <- fli_small %>%
   specify(arr_delay ~ dep_delay) %>% # alt: response = arr_delay, 
   # explanatory = dep_delay
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "slope")
ggplot(null, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = slope_hat, color = "red")  
null %>% 
  summarize(p_value = mean(stat > slope_hat) * 2)   
```

>>>>

```{r}
x_bar <- fli_small %>%
  summarize(mean(dep_delay)) %>%
  pull()
null_distn <- fli_small %>%
  specify(response = dep_delay) %>%
  hypothesize(null = "point", mu = 10) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "mean")
ggplot(data = null_distn, mapping = aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = x_bar, color = "red")
null_distn %>%
  summarize(p_value = mean(stat > x_bar) * 2)
```

@@

```{r}
x_tilde <- fli_small %>%
  summarize(median(dep_delay)) %>%
  pull()
null_distn <- fli_small %>%
  specify(response = dep_delay) %>%
  hypothesize(null = "point", med = 0) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "median")
ggplot(null_distn, aes(x = stat)) +
  geom_bar() +
  geom_vline(xintercept = x_tilde, color = "red")
null_distn %>%
  summarize(p_value = mean(stat < x_tilde) * 2)
```

@@

```{r}
p_hat <- fli_small %>%
  summarize(mean(day_hour == "morning")) %>%
  pull()
null_distn <- fli_small %>%
  specify(response = day_hour, success = "morning") %>%
  hypothesize(null = "point", p = .5) %>%
  generate(reps = 1000, type = "simulate") %>%
  calculate(stat = "prop")
ggplot(null_distn, aes(x = stat)) +
  geom_bar() +
  geom_vline(xintercept = p_hat, color = "red")
null_distn %>%
  summarize(p_value = mean(stat < p_hat) * 2)
```

@@

```{r}
null_distn <- fli_small %>%
  mutate(day_hour_logical = (day_hour == "morning")) %>%
  specify(response = day_hour_logical, success = "TRUE") %>%
  hypothesize(null = "point", p = .5) %>%
  generate(reps = 1000, type = "simulate") %>%
  calculate(stat = "prop")
```

@@

```{r}
d_hat <- fli_small %>%
  group_by(season) %>%
  summarize(prop = mean(day_hour == "morning")) %>%
  summarize(diff(prop)) %>%
  pull()
null_distn <- fli_small %>%
  specify(day_hour ~ season, success = "morning") %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>% 
  calculate(stat = "diff in props", order = c("summer", "winter"))
ggplot(null_distn, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = d_hat, color = "red")
null_distn %>%
  summarize(p_value = mean(stat < d_hat) * 2)
```

@@

```{r}
Chisq_hat <- chisq.test(table(fli_small$origin))$stat
null_distn <- fli_small %>%
  specify(response = origin) %>%
  hypothesize(null = "point", 
              p = c("EWR" = .33, "JFK" = .33, "LGA" = .34)) %>% 
  generate(reps = 1000, type = "simulate") %>% 
  calculate(stat = "Chisq")
ggplot(null_distn, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = Chisq_hat, color = "red")
null_distn %>%
  summarize(p_value = mean(stat > Chisq_hat)) 
```

@@

```{r}
Chisq_hat <- chisq.test(table(fli_small$day_hour, fli_small$origin))$stat
null_distn <- fli_small %>%
  specify(day_hour ~ origin, success = "morning") %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>% 
  calculate(stat = "Chisq")
ggplot(null_distn, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = Chisq_hat, color = "red")
null_distn %>%
  summarize(p_value = mean(stat > Chisq_hat)) 
```

@@

```{r}
d_hat <- fli_small %>% 
  group_by(season) %>% 
  summarize(mean_stat = mean(dep_delay)) %>% 
  summarize(diff(mean_stat)) %>% 
  pull()
null_distn <- fli_small %>%
  specify(dep_delay ~ season) %>% # alt: response = dep_delay, 
  # explanatory = season
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("summer", "winter"))
ggplot(null_distn, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = d_hat, color = "red")
null_distn %>%
  summarize(p_value = mean(stat > d_hat) * 2)   
```

@@

```{r}
d_hat <- fli_small %>% 
  group_by(season) %>% 
  summarize(median_stat = median(dep_delay)) %>% 
  summarize(diff(median_stat)) %>% 
  pull()
null_distn <- fli_small %>%
  specify(dep_delay ~ season) %>% # alt: response = dep_delay, 
  # explanatory = season
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in medians", order = c("summer", "winter"))
ggplot(null_distn, aes(x = stat)) +
  geom_bar() +
  geom_vline(xintercept = d_hat, color = "red")
null_distn %>%
  summarize(p_value = mean(stat > d_hat) * 2)    
```

@@

```{r}
F_hat <- anova(
               aov(formula = arr_delay ~ origin, data = fli_small)
               )$`F value`[1]
null_distn <- fli_small %>%
   specify(arr_delay ~ origin) %>% # alt: response = arr_delay, 
   # explanatory = origin
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "F")
ggplot(null_distn, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = F_hat, color = "red")  
null_distn %>% 
  summarize(p_value = mean(stat > F_hat))
```

@@

```{r}
slope_hat <- lm(arr_delay ~ dep_delay, data = fli_small) %>% 
  broom::tidy() %>% 
  filter(term == "dep_delay") %>% 
  select(estimate) %>% 
  pull()
null_distn <- fli_small %>%
   specify(arr_delay ~ dep_delay) %>% 
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "slope")
ggplot(null_distn, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = slope_hat, color = "red")  
null_distn %>% 
  summarize(p_value = mean(stat > slope_hat) * 2)   
```
